---
title: "Creating_Shiny_Apps"
author: "Matthew Martinez"
date: "4/9/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Shiny Basics

What is a Shiny app? Well, think of Shiny apps as light applets that allow you to create interactive visualizations of your data in real-time. Shiny apps allow end-users to manipulate tables and graphs, currate new data, filter data for new visualizations, and a host of other items that put the data story in the hands of users. You can find some great examples of [Shiny apps here](https://shiny.rstudio.com/gallery/). I have some personal apps that I created for demonstration purposes as well.

At the end of these few weeks you will be able to [deploy](https://www.shinyapps.io/) a live app that can be viewed on your computer, phone, tablet, or other internet device. 

library(shiny) - This brings in the library.
ui <- fluidPage() - This is the ui for the applicaton

server <- function(input, output) {}

shinyApp(ui = ui, server = server)


```{r pressure, echo=FALSE}
plot(pressure)
```

